Demystifying the Computer Science \\ PhD Admission in the US\\{\large A Handbook for International \emph{and Domestic} Students

### 2024-08-24 demystify.tex
updates

\section{How long to complete the CS PhD program?}\label{sec:time}
\sectioninfo{About 5--7 years in the US}

@@

\section{What's the difference between PhD and MS in CS?}\label{sec:phd-vs-ms}

@@

>>>>

\section{How long to complete the CS PhD program?}\label{sec:time}
\sectioninfo{About 5--7 years in the US.}

@@

\section{What's the difference between PhD and MS in CS?}\label{sec:phd-vs-ms}
\sectioninfo{MS focuses on coursework and prepares you for industry, while PhD focuses on research and prepares you for academia or research labs.}

@@

However, note that the prof. might not have the funding to buy you things. More importantly, they are not obligated to do so. It might also a need-based decision, e.g., if you need a powerful computer for your research, then the prof. might buy it for you (the lab might already has powerful servers and you can just use them for your work).  But if you just want a new computer because others have it, then the prof. might not buy it for you.
